### 2020-07-20 README.Rmd

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/eurobarometer")
```

@@

1. We import the GESIS SPSS files with the help of the [haven](https://haven.tidyverse.org/) package. In order to preserve the metadata in the files (particularly variable- and value labels, and user-defined missing values) these are converted to labelled classes.

2. We analyse the files with `gesis_metadata_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html) or `vignette("metadata")`)

@@

4. We convert the variables to a modified version of the `haven_labelled_spss` class that contains the harmonized values, harmonized labels, harmonized missing values codes of the variable with their history (original values, labels, and function applied to change them)  for reproducibility. The [eurobarometer_labelled](http://eurobarometer.danielantal.eu/articles/eurobarometer_class.html) class inherits most of the functionality of the packages [haven](https://haven.tidyverse.org/),  [labelled](https://cran.r-project.org/web/packages/labelled/vignettes/intro_labelled.html) and are expected to work well with [sjlabelled](https://strengejacke.github.io/sjlabelled/articles/labelleddata.html).

>>>>

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/retroharmonize")
devtools::install_github("antaldaniel/eurobarometer")
```

You do not need to load the [retroharmonize](http://retroharmonize.satellitereport.com/) package with `library(retroharmonize)` but eurobarometer relies on some if its classes, methods and functions.

@@

1. We import the GESIS SPSS files with the help of the adopted version of `read_spss()` from the [haven](https://haven.tidyverse.org/) package. The `haven::write_sav()` function does not work perfectly, it loses some metadata, so the best is to save you data as an `.rds` file. You can read surveys then with `read_rds()`. Both importing function will try to add important metadata to the `retroharmonize::survey()` tibble/data.frame class, including the original file name, the survey's ID and DOI.

2. We analyse the files with `gesis_metadata_create()` to understand what are the possible problems in the SPSS file and how to resolve them. (See: [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html) or `vignette("metadata")`) This is a modified version of the more generic [metadata_create](http://retroharmonize.satellitereport.com/reference/metadata_create.html) function in `retroharmonize`. See the [Working With Metadata](http://eurobarometer.danielantal.eu/articles/metadata.html) vignette for some more details.

@@

4. We convert the variables to a modified version of the `retroharmonize_labelled_spss_survey` class that contains the harmonized values, harmonized labels, harmonized missing values codes of the variable with their history (original values, labels, and function applied to change them)  for reproducibility. The [labelled_spss_survey](http://retroharmonize.satellitereport.com/articles/labelled_spss_survey.html) class inherits most of the functionality of the packages [haven](https://haven.tidyverse.org/),  [labelled](https://cran.r-project.org/web/packages/labelled/vignettes/intro_labelled.html) and are expected to work well with [sjlabelled](https://strengejacke.github.io/sjlabelled/articles/labelleddata.html).

5. The harmonization of the variable names is currently possible with retroharmonize only (See: [Harmonize Value Labels](http://retroharmonize.satellitereport.com/articles/harmonize_labels.html)). Further, Eurobarometer specific helpers will be added soon. See the article [Survey Data Harmonization](http://eurobarometer.danielantal.eu/articles/harmonization.html) as a case study.
